\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-22 main.tex
Updates from Overleaf

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$. Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to

\begin{equation}
    \label{eq:london}
    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
\end{equation}
where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).

@@

Because the sheet current has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
except at small terminals where current can be injected, one can express the sheet current in terms
of a scalar potential $g(x, y)$, called the stream function:

\begin{equation}
    \label{eq:stream}
    \vec{J}(x, y) = -\hat{z}\times\nabla g
    = \nabla\times(g\hat{z})
    = \left(\frac{\partial g}{\partial y}, -\frac{\partial g}{\partial x}\right).
\end{equation}

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function). We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:

\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z}
    \end{split}
\end{align}
where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator. (The last line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$). From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:

\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'  
    \end{split}
\end{align}

Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$. $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:

\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \vec{r}') &=  3\frac{(x-x')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \vec{r}') &=  3\frac{(y-y')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
        {4\pi[(z-z')^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.

Comparing Eq.~\ref{eq:london_stream} and Eq.~\ref{eq:field_from_kernel}, we have in the plane of the film:

\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
        = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e. $z-z'=0$ since the film is in the same plane as itself. From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:

\begin{align}
\begin{split}
    \label{eq:applied_to_stream}
    &H_{z,\,\mathrm{applied}}(\vec{r})
    = \\ &-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function.

@@

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux $\Phi_k$, with an associated circulating current $I_{\mathrm{circ},\,k}$. The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:

\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,k}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,k}[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:

\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

@@

The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:

\begin{equation}
    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
    \label{eq:fluxoid}
\end{equation}

The fluxoid vanishes for a region $S$ completely contained within a superconducting film that contains no holes or vortices, and has the same value for any region containing a given hole or collection of vortices in a superconducting film. This path-independence of the fluxoid follows from the static London equation (Eq.~\ref{eq:london}) on which the present model is based. Fluxoid quantization---the requirement that the fluxoid $\Phi^f_S=n\Phi_0$ where $n$ is an integer and $\Phi_0=h/2e$ is the magnetic flux quantum---is not automatically enforced by Eq.~\ref{eq:london}, however it can be included as an external constraint.
% However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{Tinkham2004-zn}, within this model the fluxoid is not constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:

\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

The discrete version of Eq.~\ref{eq:field_from_kernel} is

\begin{align}
\begin{split}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{(\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
    % &=\mathbf{h}_{z,\,\mathrm{applied}}
    % + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}w_jg_j,
\end{split}
\end{align}
where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top line) and the equivalent discrete sum version (bottom line).

The $n\times n$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film, and the $n\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$. Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device. $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by

\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
and $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by

\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

The matrix version of Eq.~\ref{eq:Heff_sub} is

\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh. Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have

\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        -\mathbf{K}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,k}\mathbf{h}_{z,\,\mathrm{eff},\,k}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,k}
            & \text{inside hole }k\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

@@

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}.}
    \label{fig:ring-with-slit}
\end{figure*}

>>>>

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$. Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
\end{equation}
where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).

@@

Because the sheet current has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
except at small terminals where current can be injected, one can express the sheet current in terms
of a scalar potential $g(x, y)$, called the stream function:
\begin{equation}
    \label{eq:stream}
    \vec{J}(x, y) = -\hat{z}\times\nabla g
    = \nabla\times(g\hat{z})
    = \left(\frac{\partial g}{\partial y}, -\frac{\partial g}{\partial x}\right).
\end{equation}

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function). We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z},
    \end{split}
\end{align}
where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator. (The last line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$). From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'.  
    \end{split}
\end{align}

Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$. $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \vec{r}') &=  3\frac{(x-x')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \vec{r}') &=  3\frac{(y-y')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
        {4\pi[(z-z')^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.

Comparing Eq.~\ref{eq:london_stream} and Eq.~\ref{eq:field_from_kernel}, we have in the plane of the film:
\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
        = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e. $z-z'=0$ since the film is in the same plane as itself. From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream}
    &H_{z,\,\mathrm{applied}}(\vec{r})
    = \\ &-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function.

@@

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux $\Phi_k$, with an associated circulating current $I_{\mathrm{circ},\,k}$. The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,k}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,k}[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:
\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

@@

The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
\begin{equation}
    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
    \label{eq:fluxoid}
\end{equation}

The fluxoid vanishes for a region $S$ completely contained within a superconducting film that contains no holes or vortices, and has the same value for any region containing a given hole or collection of vortices in a superconducting film. This path-independence of the fluxoid follows from the static London equation (Eq.~\ref{eq:london}) on which the present model is based. Fluxoid quantization---the requirement that the fluxoid $\Phi^f_S=n\Phi_0$ where $n$ is an integer and $\Phi_0=h/2e$ is the magnetic flux quantum---is not automatically enforced by Eq.~\ref{eq:london} for multiply-connected films, however it can be included as an external constraint.

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

The discrete version of Eq.~\ref{eq:field_from_kernel} is
\begin{align}
\begin{split}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{(\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
    % &=\mathbf{h}_{z,\,\mathrm{applied}}
    % + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}w_jg_j,
\end{split}
\end{align}
where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top line) and the equivalent discrete sum version (bottom line).

The $n\times n$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film, and the $n\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$. Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device. $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
and $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh. Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        -\mathbf{K}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,k}\mathbf{h}_{z,\,\mathrm{eff},\,k}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,k}
            & \text{inside hole }k\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

@@

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:ring-with-slit}
\end{figure*}
